### 2014-05-27 May.Rmd
create gh-pages branch

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
                     profit, delta=delta, reward=0)
````

@@

``` {r  p1}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````

>>>>

``` {r  find_dp_opt, dependson="SDP_Mat"}
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
                     profit, delta=delta, reward=0)
````

@@

``` {r  p1, dependson="tidy"}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidy"}
profits <-dt[ , sum(profit), by="reps"] 
ggplot(profits) + geom_histogram(aes(V1)) 
````

### 2014-05-27 logistic_uniform.Rmd
create gh-pages branch

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

>>>>

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0.01,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

### 2014-05-27 multiple_uncertainty.Rmd
create gh-pages branch

``` {r sethiplots, cache=FALSE}
require(reshape2)
XMAX <- 140
policy <- melt(data.frame(stock = x_grid, det=det$D[,1], low_g = opt_low$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))

dat <- subset(policy, stock < XMAX)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,XMAX, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	geom_jitter(aes(x,y, color=variable), shape='+') +
  xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```

>>>>

``` {r sethiplots, cache=FALSE}
require(reshape2)
XMAX <- 140
policy <- melt(data.frame(stock = x_grid, det=det$D[,1], low_g = opt_low$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))
dat <- subset(policy, stock < XMAX)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,XMAX, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	geom_jitter(aes(x,y, color=variable), shape='+') +
  xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```

### 2014-05-27 policycosts/costfree.Rmd
create gh-pages branch

```{r Figure4}
frac_lost <- seq(0,1, length=20)
tmp <- lapply(frac_lost, fig4, ls())
out <- melt(tmp, id=c("reps", "var", "acor"))
colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
out <- data.table(out)

Ev = out[,mean(var),by=c('penalty', 'fraction')]
SDv = out[,sd(var),by=c('penalty', 'fraction')]
Ea = out[,mean(acor),by=c('penalty', 'fraction')]
SDa = out[,sd(acor),by=c('penalty', 'fraction')]

tmp2 <- data.table(penalty = Ev$penalty, fraction = Ev$fraction, Ev = Ev$V1, Ea = Ea$V1, SDv=SDv$V1, SDa = SDa$V1)

Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b
````

>>>>

# Figure 4

```{r}
frac_lost <- seq(0,1, length=20)
```

```{r helper_fn_1}
fig4 <- function(fraction_lost){
closest <- function(x, v){
  which.min(abs(v-x))
}
dt_npv <- data.table(fees)
index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable

L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
quad_policy <- policies$quad[[apples_index["quad"]]]$D

quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
sims <- lapply(1:50, function(reps) list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"])),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            quad_policy, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none)
  ))

  #Make data tidy (melt), fast (data.tables), and nicely labeled.
  dat <- melt(sims, id=names(sims[[1]][[1]]))  
  dt <- data.table(dat)
  setnames(dt, "L1", "reps") # names are nice
  setnames(dt, "L2", "penalty_fn") # names are nice

  dt
}
```

```{r helper_fn_2} 
# Helper functions to extract the summary stats in different variables
stats_harvest <- function(dt){
v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}

stats_fishstock <- function(dt){
v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}
```

```{r helper_fn_3}
#' a simple function for reorganizing the data over the different "faction-lost" levels
get_trends <- function(tmp2){
  out <- melt(tmp2, id=c("reps", "var", "acor"))
  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
  out <- data.table(out)
  Ev = out[,mean(var),by=c('penalty', 'fraction')]
  SDv = out[,sd(var),by=c('penalty', 'fraction')]
  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
  harvest_trends <- data.table(penalty = Ev$penalty, 
                               fraction = Ev$fraction, 
                               Ev = Ev$V1, Ea = Ea$V1, 
                               SDv=SDv$V1, SDa = SDa$V1)
}
```

```{r Figure4_harvest}
sims_at_each_apple <- lapply(frac_lost, fig4)
harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
harvest_trends <- get_trends(harvest_stats)
```

```{r Figure4}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b
````

```{r Figure4S}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)

FigS4a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

FigS4b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
FigS4a
FigS4b
```

### 2014-05-27 policycosts/errors_table.Rmd
create gh-pages branch

``` {r defs}
compute_error_table <- function(r = 2, sigma = 0.2){
reduction_range = c(.1, .2, .3)
reduction <- reduction_range[r]

@@

seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- sigma              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

sigma_g <- 0.3
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)

tmp <- lapply(1:100, function(i){ 
  set.seed(i)
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
  })
tmp <- melt(tmp, id = names(tmp[[1]]))
sum(tmp$profit)

@@

>>>>

``` {r defs}
compute_error_table <- function(r, sigma){
reduction_range = c(.1, .2, .3)
reduction <- reduction_range[r]

@@

delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- sigma              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)

@@

dt$profit <- dt$profit_fishing/(1+delta)^dt$time
dt$profit_fishing_alt <- dt$profit_fishing_alt/(1+delta)^dt$time
dt$policy_cost <- dt$policy_cost/(1+delta)^dt$time
dt$policy_cost_alt <- dt$policy_cost_alt/(1+delta)^dt$time

### 2014-05-27 policycosts/writeup.Rmd
create gh-pages branch

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="test/")
opts_knit$set(upload.fun=socialR::flickr.url)
```

@@

```{r setup}
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.5            # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="writeup/")
opts_knit$set(upload.fun=socialR::flickr.url)
```

@@

```{r setup}
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

### 2014-05-27 resilience_assessment.Rmd
create gh-pages branch

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="criticaltransition/" or`

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

@@

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="resilience_assessment/" or`

``` {r  echo=FALSE, cache=FALSE}
#opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) {
#    pdf(NULL, width = width, height = height)
#})
knitcitations::cleanbib()
````

@@

    # Track the location of the stable and unstable points?

@@

### Warning signal assessment

1. Simulate timeseries before management begins, use this data to compute warning signals.  
2. Calculate the ROC curve
3. Calculate the expected profits remaining under the hypothesis that the system is not going to collapse. "D"
4. Calculate the expected profits under the assumption that the system collapses (in the next timestep?)  "C" == 0
5. Calculate the profits expected under a response to the signal.  (Say, 50% reduction in harvest). "A", "B"

Ideal response with complete information: determine the optimal policy under temporally changing f.

### 2014-05-27 unmanaged_warning.Rmd
create gh-pages branch

``` {r summarystat_roc} 
summarystat_roc <- function(A,B, summarystat_functions, reps=200){
  require(plyr)
  require(reshape2)
  Asim <- simulate(A, reps)
  Bsim <- simulate(B, reps)
  sim <- melt(Asim, id = "time")
  Bsim <- melt(Bsim, id = "time")
  names(Asim)[2] <- "rep"
  names(Bsim)[2] <- "rep"
	dat <- lapply(summarystat_functions, function(f){
	  wsA <- ddply(Asim, "rep", warningtrend, f)
  	wsB <- ddply(Bsim, "rep", warningtrend, f)
	  data.frame(null = wsA$tau, test = wsB$tau)
	})
	tidy <- melt(dat)
}

tau_dist <- summarystat_roc(A, B, list(var=window_var, acor=window_autocorr))
head(tau_dist)
```

>>>>

Compute summary stat versions

``` {r summarystat_roc} 
summarystat_roc <- function(A,B, summarystat_functions, reps=200){
  require(plyr)
  require(reshape2)
  Asim <- simulate(A, reps)
  Bsim <- simulate(B, reps)
  Asim <- melt(Asim, id = "time")
  Bsim <- melt(Bsim, id = "time")
  names(Asim)[2] <- "rep"
  names(Bsim)[2] <- "rep"
	dat <- lapply(summarystat_functions, function(f){
	  wsA <- ddply(Asim, "rep", warningtrend, f)
  	wsB <- ddply(Bsim, "rep", warningtrend, f)
	  data.frame(null = wsA$tau, test = wsB$tau)
	})
	tidy <- melt(dat)
}

dat <- summarystat_roc(A,B, list(var=window_var, acor=window_autocorr))
ggplot(dat) + geom_density(aes(value, fill=variable)) + facet_wrap(~L1)
```

### 2014-05-27 voi_May.Rmd
create gh-pages branch

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

>>>>

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list(det  = c(0,0,0), 
							low = c(0.1, .1, .1),  
							grow = c(lvl, 0, 0),
              meas  = c(0, lvl, 0), 
							imp = c(0,0,lvl), 
							gro_meas = c(lvl, lvl, 0),  
							gro_imp = c(lvl, 0, lvl),  
							meas_imp = c(0, lvl, lvl), 
							all = c(lvl, lvl, lvl))
````

``` {r loopoverall}
 allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    try(simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3]))
  })
})
````
